
\section{References}
\begin{enumerate}
  \item Altmann, S.L.: Rotations, Quaternions and Double Groups. Dover, New York (2005). ISBN13: 978-0-486-44518-2 (1986)

  \item Altmann, S.L.: Rotations, Quaternions and Double Groups. Dover, New York (2005). ISBN13: 978-0-486-44518-2, p. $16(1986)$

  \item Altmann, S.L.: Rodrigues, and the quaternion scandal. Math. Mag. 62(5), 291-308 (1989)

  \item Altmann, S.L.: Icons and Symmetries. Clarendon Press, Oxford (1992)

  \item Altmann, S.L., Ortiz, E.L. (eds.): Mathematics and Social Utopias in France: Olinde Rodrigues and his Times. History of Mathematics, vol. 28. Am. Math. Soc., Providence (2005). ISBN-10: 0-8218-3860-1, ISBN-13: 978-0-8218-3860-0

  \item Argand, J.R.: \href{http://www-history.mcs.st-andrews.ac.uk/Mathematicians/Argand.html}{http://www-history.mcs.st-andrews.ac.uk/Mathematicians/Argand.html}

  \item Argand, J.R.: Essai sur une manière de représenter les quantités imaginaires dans les constructions géométriques, 2nd edn. Gauthier-Villars, Paris (1874)

  \item Cayley, A.: The Collected Mathematical Papers, vol. I, p. 586 (1848). Note 20

  \item Cheng, H., Gupta, K.C.: An historical note on finite rotations. Trans. ASME J. Appl. Mech. 56(1), 139-145 (1989)

  \item Crowe, M.J.: A History of Vector Analysis. Dover, New York (1994)

  \item Descartes, R.: La Géométrie (1637). There is an English translation by Michael Mahoney: Dover, New York (1979).

  \item Feynman, R.P.: Symmetry and physical laws. In: Feynman Lectures in Physics, vol. 1

  \item Gauss, C.F.: Mutation des Raumes. In: Carl Friedrich Gauss Werke, Achter Band, pp. $357-$ 361. König. Gesell. Wissen. Göttingen (1900). (1819)

  \item Hamilton, W.R.: In: Conway, A.W., Synge, J.L. (eds.) The Mathematical Papers of Sir William Rowan Hamilton, vol. I, Geometrical Optics; Conway, A.W., McDonnell, A.J. (eds.) vol. II, Dynamics; Halberstam, H., Ingram, R.E. (eds.) vol. III, Algebra, Cambridge University Press, Cambridge (1931, 1940, 1967) (1833)

  \item Hamilton, W.R.: \href{http://www-history.mcs.st-andrews.ac.uk/Mathematicians/Hamilton.html}{http://www-history.mcs.st-andrews.ac.uk/Mathematicians/Hamilton.html}

  \item Hamilton, W.R.: On Quaternions: Or a New System of Imaginaries in Algebra. Phil. Mag. 3rd ser. 25 (1844)

  \item Hamilton, W.R.: Lectures on Quaternions. Hodges \& Smith, Dublin (1853)

  \item Hamilton, W.R.: Elements of Quaternions. 2nd edn. Longmans, Green \& Co, London (18991901) (Jolly, C.J. (ed.) 2 vols.)

  \item Robinson, E.: Greek and English lexicon of the New Testament. \href{http://books.google.co.uk}{http://books.google.co.uk} (1825)

  \item Rodrigues, B.O.: Des lois géométriques qui régissent les déplacements d'un système solide dans l'espace, et de la variation des coordonnées provent de ses déplacements considérés indépendamment des causes qui peuvent les produire. J. Math. Pures Appl. 5, 380-440 (1840)

  \item Tait, P.G.: Elementary Treatise on Quaternions. Cambridge University Press, Cambridge (1867) 22. Wallis, J.: \href{http://www-history.mcs.st-andrews.ac.uk/Mathematicians/Wallis.html}{http://www-history.mcs.st-andrews.ac.uk/Mathematicians/Wallis.html}

  \item Wilson, E.B.: Vector Analysis. Yale University Press, New Haven (1901)

\end{enumerate}

\section{Index}
A

Abel, Neils, 10

Abelian group, 10

Absolute value of a complex number, 17

Adding complex numbers, 16, 25

Adding quaternions, 57

Additive associativity, 11

Additive commutativity, 11

Additive form of a quaternion, 60

Additive inverse, 11

Altmann, Simon, 48, 49, 58

Argand, Jean-Robert, 33

Argand diagram, 34

Argument of a complex number, 37

Associative axiom, 5

Associative division algebras, 11

Associativity, 21

Axial vector, 58

Axioms, 5

\section{B}
Binary form of a quaternion, 60

\section{$\mathbf{C}$}
Cantor, Georg, 4

Cayley, Arthur, 91

Cayley numbers, 68,91

Characteristic equation, 133

Closed operation, 4

Closure, 21

Commutative axiom, 5

Complex conjugate, 18, 25

Complex number, 13,15

Complex number as a rotor, 41

Complex plane, 33, 34

Composite rotations, 75

Composition algebra, 91

Couple, 7

\section{D}
Descartes, René, 13

Distributive axiom, 5

Distributivity, 11, 21

Division algebra, 68

Division ring, 10, 11

\section{$\mathbf{E}$}
Eigenvalue, 110

Eigenvector, 110

Euler, Leonhard, 34

Euler angles, 120

Euler rotations, 73,75

$\mathbf{F}$

Feynman, Richard, 58

Field, 10, 21

Four-square law, 92

Frames of reference, 113

Français, Jacques, 34

Frobenius, Ferdinand Georg, 11

$\mathbf{G}$

Gibbs, Josiah Willard, 47, 52

Gimbal lock, 75

Grassmann, Hermann Günter, 52

Graves, John Thomas, 91

Group, 8

$\mathbf{H}$

Hamilton, William Rowan, 47

Hamilton's rules, 49

Hurwitz, Adolf, 92

Hurwitz's theorem, 92

I

Identity element, 21 Identity matrix, 24

Imaginary number, 13

Infinity, 4

Integers, 4

Interpolating quaternions, 114

Inverse, 21

Inverse of a complex number, 19, 26

Inverse quaternion, 65

\section{$\mathbf{J}$}
Juel, Sophus Christian, 34

\section{$\mathbf{M}$}
Matrices, 3, 67

Matrix for a complex number, 24

Member of a set, 3

Modulus of a complex number, 17

Multiplicative associativity, 11

Multiplicative identity, 11

Multiplicative inverse, 11

Multiplying complex numbers, 16

\section{$\mathbf{N}$}
$\mathrm{N}$-square identity, 92

Natural numbers, 3

Non-commutative, 6

Norm of a complex number, 17, 25, 37

Norm of a quaternion, 62

Norm of the quaternion product, 65

Normalised quaternion, 62

$\mathbf{0}$

Octaves, 91

Octonion, 92

Ordered pair, 7, 21, 53, 56

Ordered triple, 7

Orthogonal matrix, 67

P

Polar form, 37

Polar vector, 58

Powers of $i, 13$

Product of complex numbers, 16,25, 39

Pseudovector, 58

Pure quaternion, 58

$\mathbf{Q}$

Quaternion, 8, 47, 89

Quaternion algebra, 68

Quaternion as a matrix, 67 Quaternion conjugate, 61

Quaternion matrix, 101

Quaternion product, 54, 63, 93

Quaternion units, 53

Quotient of complex numbers, 18, 26, 39, 40

\section{$\mathbf{R}$}
2D rotation transform, 73

Rational numbers, 4

Real numbers, 3

Real quaternion, 57

Ring, 10

Rodrigues, Benjamin Olinde, 47

Rotating a complex number, 41

Rotating a point about an axis, 78

Rotation matrix, 24

Rotation transforms, 73

Rotors, 41

$\mathbf{S}$

Scalar, 3

Servois, François-Joseph, 51

Set, 3

Spherical interpolant, 117

Square of a complex number, 17

Square of a quaternion, 64

Square-root of $i, 19$

Subtracting complex numbers, 16, 25

Subtracting quaternions, 57

$\mathbf{T}$

3D transforms, 73

Tait, P.G., 34, 49

Tensor, 49

Transforms, 73

Two-square law, 92

$\mathbf{U}$

Unit quaternion, 59

Unit-norm quaternion, 62

$\mathbf{V}$

Vector, 49

Versor, 49

W

Wallis, John, 34

Wessel, Caspar, 34

Wilson, Edwin Bidwell, 52

